Hydra Battles and Cie

### 2021-07-22 doc/chapter-primrec.tex
add a few snippets to chapter 9

\begin{Coqsrc}
Fixpoint  extEqual (n : nat) : forall  (a b : naryFunc n), Prop :=
  match n with
    0 => fun a b => a = b
  | S p => fun a b => forall c, extEqual p (a c) (b c)
  end.
\end{Coqsrc}

@@

\index{primrec}{Types!PrimRec}
\index{primrec}{Types!PrimRecs}
\label{def:Primrec}
\vspace{4pt}
\noindent
\emph{From \href{../theories/html/hydras.Ackermann.primRec.html}{Ackermann.primRec}.}
\begin{Coqsrc}
Inductive PrimRec : nat -> Set :=
  | succFunc : PrimRec 1
  | zeroFunc : PrimRec 0
  | projFunc : forall n m : nat, m < n -> PrimRec n
  | composeFunc :
      forall (n m : nat) (g : PrimRecs n m) (h : PrimRec m), PrimRec n
  | primRecFunc :
      forall (n : nat) (g : PrimRec n) (h : PrimRec (S (S n))), 
      PrimRec (S n)
with PrimRecs : nat -> nat -> Set :=
  | PRnil : forall n : nat, PrimRecs n 0
  | PRcons : forall n m : nat, PrimRec n -> PrimRecs n m -> 
                   PrimRecs n (S m).
\end{Coqsrc}

@@

\begin{Coqsrc}
Fixpoint evalPrimRec (n : nat) (f : PrimRec n) {struct f} : 
 naryFunc n :=
  match f in (PrimRec n) return (naryFunc n) with
  | succFunc => S
  | zeroFunc => 0
  | projFunc n m pf => evalProjFunc n m pf
  | composeFunc n m l f =>
      evalComposeFunc n m (evalPrimRecs _ _ l) (evalPrimRec _ f)
  | primRecFunc n g h =>
      evalPrimRecFunc n (evalPrimRec _ g) (evalPrimRec _ h)
  end
with evalPrimRecs (n m : nat) (fs : PrimRecs n m) {struct fs} :
 Vector.t (naryFunc n) m :=
  match fs in (PrimRecs n m) return (Vector.t (naryFunc n) m) with
  | PRnil a => Vector.nil  (naryFunc a)
  | PRcons a b g gs =>
       Vector.cons _ (evalPrimRec _ g) _  (evalPrimRecs _ _ gs)
  end.
\end{Coqsrc}

@@

\vspace{4pt}
\noindent
\emph{From \href{../theories/html/hydras.Ackermann.primRec.html}{Ackermann.primRec}.}
\begin{Coqsrc}
Definition isPR (n : nat) (f : naryFunc n) : Set :=
  {p : PrimRec n | extEqual n (evalPrimRec _ p) f}.  
\end{Coqsrc}

@@

\begin{Coqsrc}
Module Alt.

Lemma zeroIsPR : isPR 0 0.
Proof.
  exists zeroFunc.
\end{Coqsrc}

\begin{Coqanswer}
1 subgoal (ID 90)

  ============================
  extEqual 0 (evalPrimRec 0 zeroFunc) 0
\end{Coqanswer}

\begin{Coqsrc}
  cbn.
\end{Coqsrc}

\begin{Coqanswer}
1 subgoal (ID 91)

  ============================
  0 = 0
\end{Coqanswer}

\begin{Coqsrc}
  reflexivity.
Qed.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma SuccIsPR : isPR 1 S.
Proof.
  exists succFunc; cbn; reflexivity.
Qed.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma pi2_5IsPR : isPR 5 (fun a b c d e => b).
Proof.
 assert (H: 3 < 5) by auto.
 exists (projFunc 5 3 H).
 cbn; reflexivity.
Qed.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma idIsPR : isPR 1 (fun x : nat => x).
Proof.
  assert (H: 0 < 1) by auto.
  exists (projFunc 1 0 H); cbn; auto.
Qed.
\end{Coqsrc}

>>>>

\input{movies/snippets/extEqualNat/extEqualDef}

@@

\index{primrec}{Types!PrimRec}
\index{primrec}{Types!PrimRecs}
\label{def:Primrec}
\vspace{4pt}
\noindent
\emph{From \href{../theories/html/hydras.Ackermann.primRec.html}{Ackermann.primRec}.}

\input{movies/snippets/primRec/PrimRecDef}

@@

\input{movies/snippets/primRec/evalPrimRecDef}

@@

\input{movies/snippets/primRec/isPRDef}

@@

\input{movies/snippets/PrimRecExamples/zeroIsPR}

@@

\input{movies/snippets/PrimRecExamples/SuccIsPR}

@@

\input{movies/snippets/PrimRecExamples/pi25IsPR}

@@

\input{movies/snippets/primRec/idIsPR}
